Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-06 longSC.tex
magnetite

\begin{equation}
E\frac{\mathrm{d}^3N}{\mathrm{d}p^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

@@

We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data qualitatively but it cannot describe the data quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
In the case of NSC(3,2), the hydrodynamic calculations underestimate the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small. 
As for NSC(4,2), the model calculations overestimate the result in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%. However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges. 
While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

@@

While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do a quantitative comparison of individual flow harmonics $v_n$ to the various models.

>>>>

\begin{equation}
E\frac{\mathrm{d}^3N}{\mathrm{d}\bold{p}^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

\noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

@@

We list here the important findings from the model comparisons to the centrality dependence of SC($m$,$n$) and NSC($m$,$n$):
\begin{enumerate}[(i)]
	\item All the VISH2+1 model calculations with large $\eta/s$ fail to capture the centrality dependence of the correlations regardless of the initial conditions.
	\item Among the VISH2+1 model calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions captures the data qualitatively, but not quantitively for most of the centrality ranges.
	\item The NSC(3,2) observable is sensitive mainly to the initial conditions, while the other observables are sensitive to both the initial conditions and the temperature dependence of $\eta/s$.
	\item The correlation strength between $v_3$ and $v_2$ and between $v_4$ and $v_3$ (NSC(3,2) and NSC(4,3)) is significantly underestimated in hydrodynamic model calculations.
	\item The sign of NSC(3,2) in 0--10\% central collisions was found to be different in the data and the hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.
	%\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>~20\%$ within the errors. This hierarchy is reproduced well both by hydrodynamic and AMPT model calculations.

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%. However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges. 
While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

@@

While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do quantitative comparison of individual flow harmonics $v_n$ to the various models.
